prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-06 inst/MyArticle/paper.Rmd
Add formular 1 and 2 as eqmarray

# Methods

@@

Given a linear model contrasts can be computed by $\hat{\beta_{c}} = \sum l\beta_{m}$ and $\textrm{var} \hat\beta_c = l\sigma^2 (X^T X)^{-1} l^T$, with $X$ being the design matrix, $\beta_m$ the model parameters and $l$ an array of coefficients. The degrees of freedom for the contrast are equal to the residual degrees of freedom of the linear model.

>>>>

\newpage
# Methods

@@

Given a linear model contrasts can be computed by 
\begin{eqnarray} 
\hat{\beta_{c}} &=& \sum l\beta_{m} 
\end{eqnarray}

and

\begin{eqnarray} 
\textrm{var} \hat\beta_c &=& l\sigma^2 (X^T X)^{-1} l^T
\end{eqnarray}

with $X$ being the design matrix, $\beta_m$ the model parameters and $l$ an array of coefficients. The degrees of freedom for the contrast are equal to the residual degrees of freedom of the linear model.
